API design for machine learning software: experiences from the scikit-learn project

### 2013-10-18 paper.tex
change back to my old affiliation
... after discussion with my new boss, who said work performed at UvA
should be credited to UvA. That saves a footnote :)
drop the SVM acronym altogether
The only thing we have to explain now is SVC, which was previously
unexpanded.

\affil[1]{Netherlands eScience Center}
\affil[2]{University of Liège}
\affil[3]{Kobe University}
\affil[4]{Parietal, INRIA Saclay}
\affil[5]{University of Bonn}
\affil[6]{University of Bucharest}
\affil[7]{Ciuvo GmbH}
\affil[8]{Institut Mines-Telecom, Telecom ParisTech, CNRS LTCI}
\affil[9]{University of Ballarat}
\affil[10]{University of Washington}
\affil[11]{Samsung Electronics Research Institute}

@@

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named hyper-parameter values
(e.g., the $C$ constant in Support Vector Machines, SVM)
and can be considered a function
that maps these values to actual learning algorithms.
The constructor does not see any actual data.
All it does is attach the given parameters to the object.
For the sake of model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
Default hyper-parameter values are provided for all built-in estimators.
These defaults are set to be relevant in many common
situations in order to make estimators effective \textit{out-of-box}.

@@

The code in Figure~\ref{svm-gridsearch} shows how to find
hyper-parameter settings for an SVM classifier (SVC)
that maximize $F_1$ score
through 10-fold cross-validation on the training set.
Two distinct hyper-parameter grids are
considered for the linear and radial basis function (RBF) kernels;
an SVM with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.

>>>>

\affil[1]{ISLA, University of Amsterdam}
\affil[2]{University of Liège}
\affil[3]{Kobe University}
\affil[4]{Parietal, INRIA Saclay}
\affil[5]{University of Bonn}
\affil[6]{University of Bucharest}
\affil[7]{Ciuvo GmbH}
\affil[8]{Institut Mines-Telecom, Telecom ParisTech, CNRS LTCI}
\affil[9]{University of Ballarat}
\affil[10]{University of Washington}
\affil[11]{Samsung Electronics Research Institute}

@@

Estimator initialization and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of named hyper-parameter values
(e.g., the $C$ constant in support vector machines)
and can be considered a function
that maps these values to actual learning algorithms.
The constructor does not see any actual data.
All it does is attach the given parameters to the object.
For the sake of model inspection, hyper-parameters are set as public attributes,
which is especially important in model selection settings.
Default hyper-parameter values are provided for all built-in estimators.
These defaults are set to be relevant in many common
situations in order to make estimators effective \textit{out-of-box}.

@@

The code in Figure~\ref{svm-gridsearch} shows how to find
hyper-parameter settings for an support vector classifier (SVC)
that maximize $F_1$ score
through 10-fold cross-validation on the training set.
Two distinct hyper-parameter grids are
considered for the linear and radial basis function (RBF) kernels;
an SVC with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.
